\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-08-15 NAR_DRAFT.tex
check in

\subsection{Real Data}
\begin{itemize}
  \item aml31 \cite{Griffith2015}
  \item item used only the platinum calls for evaluation
  \item Shi2018 \cite{Shi2018}
  \item used the gold standard calls, and combined all six biological replicates 
\end{itemize}

>>>>

\subsection{Real Data}
We analyzed two real data sets, one from an acute myeloid leukemia, and one from a multi-region sequencing experiment in breast cancer \cite{Griffith2015,Shi2018}.
We downloaded the primary and tumor bam files generated for the whole genome sequences in \cite{Griffith2015}, from dbGaP accession number phs000159.v8.p4.
\citet{Griffith2015} generated a platinum set of variant calls for this primary tumor, which we obtained from supplementary materials, and used for our true positive dataset.
The whole exome sequencing bam files generated by \cite{Shi2018} were downloaded from NCBI SRA no. SRP070662.
\citet{Shi2018} generated a gold set of variant calls for each tumor region sequenced, which we obtained from supplementary materials and used for our true positive dataset.
We called variants using Mutect 1.1.7 with the same parameters as described above, except that both of these data sets were originally aligned to GRCH37, and we used that reference here.

\begin{itemize}
  \item aml31 \cite{Griffith2015}
  \item item used only the platinum calls for evaluation
  \item Shi2018 \cite{Shi2018}
  \item used the gold standard calls, and combined all six biological replicates 
\end{itemize}
